---
name: Christopher Wituik
position: "Registered Nurse | Epidemiologist | Infection Control Specialist"
address: "51 Dacotah Street. St. Catharines, ON"
phone: +1 289-456-4242
www: 
email: "christopher.wituik@gmail.com"
twitter: cwituik
github: 
linkedin: christopherwituik
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
docname: Resume
headcolor: 414141
#headcolor: 009ACD
aboutme: "A Registered Nurse and epidemiologist focusing on the prevention and control of infections and communicable diseases. I have a strong interest in epidemiologic methods, study design, statistical programming, data visualization, and knowledge translation. I am experienced with outbreak investigation and containment, analysis of communicable and non-communicable disease data, and clinical nursing."
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```
# Education

```{r}
library(tibble)
tribble(
   ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Master of Science in Epidemiology", "London School of Hygiene & Tropical Medicine", "London, England", "November 2019", "Select coursework:    Advanced Statistical Methods in Epidemiology, Epidemiology of Communicable Disease, Modelling and the Dynamics of Communicable Diseases",
    "Master of Science in Epidemiology", "London School of Hygiene & Tropical Medicine", "London, England", "November 2019", "Research Project: Impact of Police Contact on Access to Hepatitis C Care Among People Who Inject Drugs in Vancouver, Canada",
     "Master of Science in Epidemiology", "London School of Hygiene & Tropical Medicine", "London, England", "November 2019", "Supervisors: Dr. David Prieto-Merino & Dr. Lianping Ti",
    "Bachelor of Science in Nursing", "McMaster University", "Hamilton, ON", "June 2015", "BScN Recognition Award – 2015",
      "Bachelor of Science in Nursing", "McMaster University", "Hamilton, ON", "June 2015", "Cathy Flis Memorial Award, BScN Recognition Award – 2014",
  "Diploma - Practical Nursing", "Mohawk College", "Hamilton, ON", "December 2011", "Honours graduate"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Select Employment and Academic Experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "RN Infection Control Professional", "Infection Prevention & Control - St. Joseph's Healthcare Hamilton", "Hamilton, ON", "June 2018 - Present", "IPAC Lead for COVID-19 readiness and response efforts in the Emergency Department including policy and process development, education, and consultation.",
   "RN Infection Control Professional", "Infection Prevention & Control - St. Joseph's Healthcare Hamilton", "Hamilton, ON", "June 2018 - Present", "Preventing and controlling transmission and outbreaks of epidemiologically significant organisms, monitoring and interpreting infection rates.",
    "RN Infection Control Professional", "Infection Prevention & Control - St. Joseph's Healthcare Hamilton", "Hamilton, ON", "June 2018 - Present", "Investigating viral respiratory outbreak trends; engaging in data extraction, cleaning, analysis, and visualization with R studio.",
   "RN Infection Control Professional", "Infection Prevention & Control - St. Joseph's Healthcare Hamilton", "Hamilton, ON", "June 2018 - Present", "Engaging in knowledge dissemination, education, and collaboration with various professional disciplines and members of the public.",
  "Graduate Student Research Assistant", "BC Centre on Substance Use (BCCSU)", "Vancouver, BC", "July 2019", "Analyzed two longitudinal cohorts, the Vancouver Injection Drug Users Study
(VIDUS), and the AIDS Care Cohort to Evaluate Exposure to Survival Services (ACCESS) to evaluate the impact of police contact on access to hepatitis C care among people who inject drugs.",
 "Graduate Student Research Assistant", "BC Centre on Substance Use (BCCSU)", "Vancouver, BC", "July 2019", "Independently conceived of study question; conducted data cleaning, coding, and analysis; and wrote report detailing methods, results, and interpretation.",
 "Graduate Student Research Assistant", "BC Centre on Substance Use (BCCSU)", "Vancouver, BC", "July 2019", "Achieved a working knowledge of with R statistical software through independent learning in order to conduct analysis as per BCCSU policy.",
"RN Infection Control Professional", "Infection Prevention & Control - Brant Community Healthcare System", "Brantford, ON", "March 2017 - May 2018", "Improved surveillance system through discovering an issue with patient-day calculations and collaborated with the Health Records department to ensure provision of accurate denominators for calculation of C. difficile infection rates.",
"RN Infection Control Professional", "Infection Prevention & Control - Brant Community Healthcare System", "Brantford, ON", "March 2017 - May 2018", "Designed and implemented a cross-sectional study of Catheter-Association Urinary Tract Infections. Engaged in knowledge dissemination to internal stakeholders to improve urinary catheter management throughout the organization.",
"RN Infection Control Professional", "Infection Prevention & Control - Brant Community Healthcare System", "Brantford, ON", "March 2017 - May 2018", "Invited to sit on the Brant Community Healthcare System Research Ethics Committee. Reviewed multiple clinical studies for methodological and ethical rigor.",
"Clinical Nursing", "Hamilton Health Sciences, St. Joseph's Healthcare Hamilton, Victorian Order of Nurses", "Hamilton, ON", "2012 - 2017", "Honed leadership, organization and prioritization skills which allow me to adapt to rapidly changing circumstances",
"Research Assistant", "Collaboratory for Research on Urban Neighbourhoods, Community Health, and Housing - McMaster University", "Hamilton, ON", "2013 - 2014", "Developed a working knowledge of questionnaire design, interviewing, data coding and entry, data checks, and participant recruitment",
"Research Assistant", "Collaboratory for Research on Urban Neighbourhoods, Community Health, and Housing - McMaster University", "Hamilton, ON", "2013 - 2014", " Administered a standard questionnaire to ascertain perceptions of community, neighbourhood, and health." 

) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Certification, Registration, and Professional Development

```{r}
tribble(
  ~ role, ~ company, ~ dates,
"Certification in Infection Control", "Certification Board of Infection Control and Epidemiology (CBIC)", "2019 - Present",
"Registered Nurse", "College of Nurses of Ontario (#15091963)", "2015 - Present",
"TCPS 2: CORE Course on Research Ethics", "Government of Canada", "June 2019"
) %>% 
  detailed_entries(company, dates, role)
```

# Professional Organizations 

```{r}
tribble(
  ~ role, ~ company, ~ dates,
"Association of Public Health Epidemiologists of Ontario (APHEO)", "Affiliate Member", "2016 - Present",
"Infection Prevention & Control Canada (IPAC Canada)", "Member", "2017 - Present",
"Registered Nurses Association of Ontario (RNAO)", "Member", "June 2019"
) %>% 
  detailed_entries(company, dates, role)
```

# Volunteer Experience

```{r}
tribble(
  ~ role, ~ company, ~ dates,
"COVID-19 Epidemiology Volunteer", "London School of Hygiene & Tropical Medicine", "2020 - Present",
"Harm Reduction Volunteer", "Positive Living Niagara - Streetworks Outreach Program and Consumption and Treatment Services", "2017 - Present",
"RPN-BScN Stream Representative / Education Chairperson", "McMaster University Nursing Students’ Society", "2012 - 2015"
) %>% 
  detailed_entries(company, dates, role)
```

# Skills

## Technical Skills

* Data management and entry: Microsoft Excel, EpiData
* Statistical analysis and data visualization: Stata, R, developing competence in SAS and Tableau
* Visuals and presentations: Microsoft PowerPoint

## Languages
* English (native); French (beginner)

# Publications

```{r}
tribble(
 ~ name, ~ journal, ~ date, ~type, ~ bib,
  "A case for integrating substance use harm reduction into IPAC practice in acute care settings", "Canadian Journal of Infection Control", "November 2019", "Letter to the Editor", "\\textbf{Wituik, C}. (2019). A case for integrating substance use harm reduction into IPAC practice in acute care settings. Canadian Journal of Infection Control, 34(3), 146–147."
) %>%
  detailed_entries(journal, date, name, type, bib, .protect = F)
  
```

